\chapter{Debug}	\label{chapter:debug}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\texttt{Print}}	\label{section:print}

\subsection{Description: Print Twice.}

\paragraph{Effect:}
The \text{Print} may be executed twice (unexpectedly).

\paragraph{Cause:}
The reason is that ``TLC prints its output once during the generation of the state space 
and then again when reconstructing the counter-example trace that leads to the violation.''

\paragraph{Solution:}

\paragraph{Reference:} 
\href{https://groups.google.com/forum/#!topic/tlaplus/xUTjiMq3s3E}
{Unexpected \texttt{Print} Output @ tlaplus-googlegroup}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parse}	\label{section:parse}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Checking}	\label{section:mc}

\subsection{Description: Model is Stuck in the 'modelchecking' State.}

\paragraph{Effect:}
I run the model, it gets stuck in a "modelchecking" state. 
I can't stop or restart the model checker. 
I have to restart the entire toolbox to reset the model's state.

\paragraph{Cause:}
The model is wrong.
For example, use 'a'. 

\paragraph{Solution:}
Use ``a''.

\paragraph{Reference:}
\href{https://github.com/tlaplus/tlaplus/issues/143}{Model is stuck in 'modelchecking' state @ tlaplus-googlegroup}.

\paragraph{Effect:}
I run the model, it gets stuck in a "modelchecking" state. 
I can't stop or restart the model checker. 
I have to restart the entire toolbox to reset the model's state.
{\it A .tla source file which is included by ``EXTENDS'' is missing in the Model folder.}

\paragraph{Cause:}
The project structure is broken.

\paragraph{Solution:}